Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-05 paper/paper.tex
merge Shengtao's branch
new figure

%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
\blue{We need to distinguish ourself in the problem to solve.}
In this paper, we do not limit our study to just finding an MIS and its size. 
We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
These properties include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.
% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
% and enumerating independent sets at a give size or what we call computing \textit{properties}.
Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.

@@

>>>>

%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
\blue{We need to distinct ourself in the problem we want to solve.}
In this paper, we do not limit our study to just finding an MIS and its size. 
We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
These properties include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.
% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
% and enumerating independent sets at a give size or what we call computing \textit{properties}.
Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.

@@

\begin{figure}[t] 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
    \caption{Square square entropy constants for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $1000$.}
    \label{fig:lattices}
\end{figure}
